Evaluation of performances

### 2021-08-24 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE,     verbose = TRUE)

df_tab %>%
  xtable::xtable(
    type = "latex",
    caption = "Test fold performances in RMSE (p.p.) for learner SVM on the HR dataset without using a filter, showcasing performance variance on the fold level. For each row, the model was trained on observations from all others plots but the given one and tested on the observations of the given plot.",
    label = "tab:svm-single-fold-perf"
  ) %>%
  print(
    file = here::here("docs/00-manuscripts/ieee/performance-svm-single-plot.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Best ten results among all learner-task-filter combinations, sorted in decreasing order of RMSE (p.p.) and their respective standard error (SE).",
    label = "tab:perf-top-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-top-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL,
    sanitize.text.function = function(x) {
      x
    }
  )

@@

# save as latex table
table2 %>%
  xtable(
    type = "latex",
    caption = "The overall best individual learner performance across any task and filter method for RF, SVM, XGBoost, Lasso and Ridge, sorted ascending by RMSE (p.p.) including the respective standard error (SE) of the cross-validation run.",
    label = "tab:best-learner-perf"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-best-per-learner.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    scalebox = 0.90,
    caption.placement = "top",
    timestamp = NULL,
    sanitize.text.function = function(x) {
      x
    }
  )

@@

# save as latex table
table3 %>%
  ungroup() %>%
  arrange(desc(RMSE)) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Worst ten results among all learner-task-filter combinations, sorted in decreasing order of RMSE (p.p.) and their respective standard error (SE).",
    label = "tab:perf-worst-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-worst-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL,
    sanitize.text.function = function(x) {
      x
    }
  )

@@

# save to file
table4 %>%
  print(
    file = here("docs/00-manuscripts/ieee/tune-perc-sel-features.tex"),
    include.rownames = FALSE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL,
    booktabs = TRUE,
    # important to treat content of multirow as latex content
    sanitize.text.function = force
  )

>>>>

df_tab %>%
  xtable::xtable(
    type = "latex",
    caption = "Test fold performances in RMSE (p.p.) for learner SVM on the HR dataset without using a filter, showcasing performance variance on the fold level. For each row, the model was trained on observations from all others plots but the given one and tested on the observations of the given plot.",
    label = "tab:svm-single-fold-perf"
  ) %>%
  print(
    file = here::here("docs/00-manuscripts/mdpi/performance-svm-single-plot.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Best ten results among all learner-task-filter combinations, sorted in decreasing order of RMSE (p.p.) and their respective standard error (SE).",
    label = "tab:perf-top-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/mdpi/performance-top-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL,
    sanitize.text.function = function(x) {
      x
    }
  )

@@

# save as latex table
table2 %>%
  xtable(
    type = "latex",
    caption = "The overall best individual learner performance across any task and filter method for RF, SVM, XGBoost, Lasso and Ridge, sorted ascending by RMSE (p.p.) including the respective standard error (SE) of the cross-validation run.",
    label = "tab:best-learner-perf"
  ) %>%
  print(
    file = here("docs/00-manuscripts/mdpi/performance-best-per-learner.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    scalebox = 0.90,
    caption.placement = "top",
    timestamp = NULL,
    sanitize.text.function = function(x) {
      x
    }
  )

@@

# save as latex table
table3 %>%
  ungroup() %>%
  arrange(desc(RMSE)) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Worst ten results among all learner-task-filter combinations, sorted in decreasing order of RMSE (p.p.) and their respective standard error (SE).",
    label = "tab:perf-worst-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/mdpi/performance-worst-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL,
    sanitize.text.function = function(x) {
      x
    }
  )

@@

# save to file
table4 %>%
  print(
    file = here("docs/00-manuscripts/mdpi/tune-perc-sel-features.tex"),
    include.rownames = FALSE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL,
    booktabs = TRUE,
    # important to treat content of multirow as latex content
    sanitize.text.function = force
  )
